---
title: "R in an Hour Report"
format:
  html:
    toc: true
    toc_float: true
    number-sections: true
    self-contained: true 
editor: visual
---

```{r}
#| echo: false
#| warning: false

######################
# Welcome to Quarto! #
######################

# This is quarto, think of it as an extention to R
# Where before when we produced charts and tables they appeared in a 
# viewing pane.
# Quarto allows us to create documents, reports and dashboards.
# Personally I am fond a good quality report with text that outlines 
# the analysis and uses graphs and tables to support any hypohesis

# Quarto allows output into a variety of formats, but all the cool kids
# use HTML.  It follows accessibility guidelines and can be read by 
# screen readers, it allows for interactive elements and resizes depending
# on the user, such as you could send the interative report we are
# going to make to your phone and it would work there.

# Word, powerpoint, pdf are also supported.

######################################################

# The basis of quarto is that it is broken down into chunks
# We have code chunks where we write code
# And text chuncks where we write text

# CODE STARTS

# lets load in our libraries again

# Specify required packages
my_packages <- c("tidyverse",
                 "NHSRdatasets", 
                 "NHSRplotthedots",
                 "gt",
                 "scales",
                 "pacman") 

# Extract not installed packages
not_installed <- my_packages[!(my_packages %in% installed.packages()[ , "Package"])]  

# Install not installed packages
if(length(not_installed)) install.packages(not_installed)   

# Load all packages
pacman::p_load(char = my_packages) 

# this time we already have the libraries installed, 
# we just need to call them so it takes a fraction of the time

# Load  -  monthly A&E data from NHSE datasets
data("ae_attendances")

# have a look at the AE attendances data
# pick 3 org codes at random and add them into this vector

report <- c('','','')

# eg: 
# report <- c('RF4','RLN','RQ6')
# (remember R is case sensitive)

# we are going to use the median summary we ran previously

# lets create an object of that summary
ae_summary <- ae_attendances |> 
  filter(org_code == report) |>
  summarise(median_average = median(attendances),
            .by = c(org_code, type)) |> 
  pivot_wider(id_cols = org_code, 
              names_from = type, 
              values_from = median_average,
              names_sort = TRUE)

# we will then make that into a table
summary_table <- ae_summary |>
  gt() |>
  sub_missing(
    columns = everything(),
    rows = everything(),
    missing_text = "-"
  ) |>
  fmt_auto() |>
  tab_spanner(
    label = "Attendance Type",
    columns = c("1", "2", "other")
  ) |>
  tab_header(
    title = paste0(
      "Median Attendances by type for providers ",
      paste0(report, collapse = " ")
    ),
    subtitle = paste0(
      "Covers period: ", min(ae_attendances$period), " to ", max(ae_attendances$period)
    )
  ) |>
  tab_footnote(
    footnote = md("*Data taken from NHS-R datasets*")
  ) |>
  cols_label(
    org_code = "Provider Code",
    other = "Other"
  )

###

# Now lets make a spc chart for each of your sites for each of the 
# attendance types, but seeing as we will only be changing the type
# we can turn this into a function

spc_plt_function <- function(input_type) {
ae_attendances |> 
  filter(type == input_type, 
         org_code == report,
         period > as.Date("2018-04-01")) |>
  ptd_spc(value_field = attendances, 
          date_field = period, 
          improvement_direction = "decrease",
          facet_field = org_code) |>
  ptd_create_ggplot(point_size = 2,
                    x_axis_date_format = "%b-%y")
  }


```

# Report on AE Attendances for sites `r paste0(report, collapse = " ")`

Report on AE attendances

This report shows the median number of attendances and a SPC graph to show variation and trends over time.

## Table of median attendances by type

```{r}
#| echo: false

# we are simply going to call our table object and so it will be placed here

summary_table

```

## Attendance Trends

These charts show trends within SPC charts.  

::: {.panel-tabset group="attendances"}  
### Type 1

```{r}
#| echo: false
#| warning: false

# likewise we are just going to call our plot function and 
# it will put our chart here
spc_plt_function('1')

```


### Type 2

```{r}
#| echo: false
#| warning: false

# likewise we are just going to call our plot function and 
# it will put our chart here
spc_plt_function('2')

```

### Type Other

```{r}
#| echo: false
#| warning: false

spc_plt_function('other')

```
::: 

# Caveats and contact details

Data is completely synthetic and taken from NHS-R training datasets.

:::{.callout-note collapse=true appearance='default' icon=true}
## Information (click to expand)

> **Contact**\
> [**Simon Wellesley-Miller**](mailto:Simon.Wellesley-Miller@nhs.net)\
> *Senior Analytical Manager*\
> *South West Intelligence and Insights Team*\
> `r format(Sys.Date(), "%d %B %Y")`

:::

```{r}
#| echo: false

# now what would happen if we choose different 
# org codes or even if we added another one or two?

# see how you could add additional variables and add sections for 
# admissions and breaches

# would could even automate some summary headline text to highlight
# outliers or areas of concern or success
```

